Are Solar Panels Commodities? A Bayesian Hierarchical Approach to Detecting Quality Differences and Asymmetric Information.

### 2019-04-10 ejor_submission/R&R/replyToEditor.txt

Dear Prof. Borgonovo,

Thank you for the opportunity to revise and resubmit my article, "Are Solar Panels Commodities?" to the European Journal of Operational Research.

I have done a thorough revision based on the comments of the three referees. Attached you will find detailed, point-by-point replies to each of the reviewer's suggestions and critiques in addition to the revised article.

I wish to highlight a few of the main changes to the article. As you mentioned in your letter to me, referee 2 was particularly critical and felt that the article lacked a decision-making perspective. In addition, the referee felt a lack of methodological novelty. I have taken the referee's critique to heart, and agree that the initial submission did not do an adequate job of conveying the article's relevance to decision makers nor did it sufficiently convey the articles methodological novelty. A substantial part of the revision consists of righting these weaknesses.

Referee 2 is correct in suggesting that the article could, thematically, also fit into a pure economics or finance journal. But I chose to submit to a top operations research journal, in part, because of the practical implications of the research to decision makers. As an example of how I have tried to convey this in the revision, I write on p.2 :

  From the perspective of a purchasing manager responsible for procuring solar panels, whether panels can be considered a commodity is of great importance. If panels are known to be commodities with standardised quality and similar pricing, then the decision for purchasing manager is substantially simplified. They need only to decide on the observable form factor, for example dimension and capacity. In addition, purchasing managers responsible for large projects with long lead times could make use of forward markets to hedge price movements. On the other hand, if solar panels are known to vary significantly by quality, then the decision becomes substantially more complex and costly. Purchasing managers would need to weigh the price of panels against expected quality. They may also need to make use of specialised engineering firms that test and certify panel quality. Since the purchasing decision is likely to be linked to a specific manufacturer, the purchasing manager is subject to risks such as bankruptcy or other supply disruption associated with that firm.

The methodological focus of operations research is another reason I would prefer EJOR as an outlet over a finance or economics journal. Bayesian methods are generally rare in economics and finance, apart from a few small subfields. Hierarchical Bayesian models are even more sparse. On the other hand, hierarchical Bayesian models have recently become prominent in the operations research field, and in EJOR in particular. In the revision I have worked at highlighting the relative novelty of the hierarchical Bayesian model I use, as well as presenting a more extensive review of the recent applications of hierarchical Bayes models in the operations research field. For example, on pages 4-5 I write:

  ... I use a Bayesian hierarchical model estimated using Markov Chain Monte Carlo (MCMC) simulation techniques. Bayesian hierarchical models have long been one of the primary tools in statistical decision theory (Berger, 1985). This form of modelling is increasingly common in operations research and management science. One of the main advantages is superior out-of-sample predictive properties with data with distinct groupings. Recent advances in computation have also allowed for the construction and simulation of increasingly complex models. In particular, I use the Stan probabilistic programming language (Stan Development Team, 2014) that makes use of Hamiltonian Markov Chain Monte Carlo (MCMC) (MacKay, 2003)and a No-U-Turn sampler (Homan and Gelman, 2013). Unlike earlier MCMC simulation routines and software, notably Gibbs sampler, Hamiltonian MCMC is able to reach convergence for models, like the one I present in this article, with several hierarchies. Importantly, it is not necessary to use conjugate distributions, opening up to a wider variety choice of prior distributions (Kruschke, 2014).

Later I write:

  In part due to increasing computational tractability, Bayesian hierarchical models have recently become a common and useful tool in the operations research field. A common application is to incorporate expert opinion into quantitative decision models (Rufo et al., 2010; Szwed et al., 2006; Utkin, 2006). In this application, the Bayesian hierarchical model is flexible enough to aggregate the information of the expert opinions while also being able to explicitly handle and propagate the uncertainty in these opinions. Hierarchical models have also been used to identify default risk among lenders and improve credit scoring models (Liu et al., 2015; Bhattacharya et al., 2019). In this context, the hierarchical Bayesian models are found to provide superior out-of-sample prediction for the censored sample of the data. Other operations research related applications include a fund manager's portfolio selection problem (Soyer and Tanyeri, 2006; Bodnar et al., 2017) and conjoint analysis in operations management (Karniouchina et al., 2009; Gensler et al., 2012). A commonality among all these applications is the need to aggregate information from heterogenous groups without over-fitting the data with many fixed effects.

I am happy to address any further questions or issues you or the referees should have with the revised paper. I thank you for your time and consideration.

Best wishes,

Johannes Mauritzen

### 2019-07-02 ejor_submission/R&R/revision_mauritzenApril19.tex
Final push after acceptance

\title{Are Solar Panels Commodities? Evidence of Quality Differences and Asymmetric Information from California}
\author{Johannes Mauritzen\thanks{BI Norwegian Business School, johannes.mauritzen@bi.no, \url{http://jmaurit.github.io}}}

@@

\begin{abstract}
Solar panels should not be considered commodities. Quality differences, as measured directly by degradation of production over time, are found between manufacturers. I test implications from the theory of asymmetric information of quality and find evidence that: 1.) Solar systems with high-information third party owners display higher quality than those owned by low-information hosts. 2.) The price of solar panels that are owned by high-information owners are more highly correlated to quality. I use random effects models estimated by maximum likelihood and Bayesian hierarchical models estimated by Markov Chain Monte-Carlo.
\end{abstract}

@@

More formally, a commodity is generally defined by a certain degree of fungibility. That is, the good from a certain producer will be largely interchangeable with the good of another producer. Brent crude oil produced by Statoil from the Norwegian North Sea and that produced by BP from the UK North Sea are sold at the same price, as established by an exchange. In a similar manner, the electricity produced by a solar panel at a certain location and time can also be considered a commodity.

@@

Furthermore, if significant quality differences between manufacturers exists, then the characteristics of solar panel investments suggest the possibility of asymmetric information of quality in the market.

@@

The market for rooftop solar panels can be expected to be particularly vulnerable to issues of asymmetric information on quality. Solar panels can be characterized as an ``experience'' good, where an investor/consumer needs to learn about the quality through use. In particular, poor quality panels will tend to show a higher degradation of output over time than high quality panels. Even then, solar panel owners may find it difficult to measure the degradation as it can happen gradually, over many years.

@@

From this informal model of information asymmetry in the market for solar panels, a testable implication arises. The quality of panels, as measured by degradation of output over time, would be predicted to be higher in the systems owned by the high-information owners (third-party-owner) who can discern between low and high quality solar panels. Conversely, the basic theory of asymmetric information suggests that lower quality panels will tend to push out higher quality panels in the presence of low-information buyers who can not discern quality, and therefor make purchasing decision solely on price.

A related prediction from the theory of asymmetric information of quality is that the cost of solar panel systems should have a higher degree of correlation with quality when the owner is a high-information type. Because a high-information owner can, by definition, differentiate between high and low quality panels.

@@

I have three nested predictions that I wish to test:

@@

The data has a natural hierarchy of between 36 and 60 monthly observations within the 3000-plus solar panel systems, which in turn can be grouped according to relevant characteristics such as whether they are host-owned or third-party owned. Because these groupings display considerable heterogeneity in sample size, mean values and variance, it is natural to model the relevant structure of the data directly. For relatively parsimonious models with one or two hierarchies and few covariates, I can use linear mixed effects models (LMEM) estimated by maximum likelihood. However, for richer models with all relevant hierarchies, maximum likelihood becomes impractical.

As a solution, I use a Bayesian hierarchical\footnote{Sometimes also called multilevel modeling or random effects modeling} model estimated using Markov Chain Monte Carlo (MCMC) simulation techniques. This form of modeling has long been established in multivariate dynamic modeling in macroeconomics \citep{doan_forecasting_1984, litterman_forecasting_1986,sims_bayesian_1998, canova_forecasting_2004},  but is also increasingly common in microeconomics and corporate finance. One of the main advantages is superior out of sample predictive properties with data with distinct groupings. For example \citet{dehejia_was_2003} uses a Bayesian hierarchical model to evaluate multiple programs at different sites. By incorporating ``predictive uncertainty'' by way of a hierarchical model, the impact of the sites, which otherwise is estimated to be significant with a fixed-effects model, disappears. \citet{meager_understanding_2018} presents a more recent application in the microeconomics litterature. She uses a hierarchical model to aggregate studies of microcredit expansion in developing countries in order to estimate an overall treatment effect with ``external validity,'' that is the degree to which an estimated treatment effect generalizes to other populations.

Within the field of corporate finance, \citet{jones_mutual_2005} uses a hierarchical model to study returns of mutual funds, arguing that estimates of long-run returns of any single fund should be informed, by way of a higher-level distribution, of the returns of the population of other mutual funds. In a study with parallels to my own, \citet{korteweg_skill_2017} uses a Bayesian hierarchical model to study persistence of returns in the private equity sector both between and within firms, where persistence is measured by excess variation between firms as captured by firm-level parameters (or random effects) that are drawn from a higher-level distribution. If returns are thought of as the converse of production degradation, then the existence of persistence of returns can be thought of as the converse of quality differences.

@@

The property of hierarchical models that allows for improved predictive performance with the presence of groupings in the data is regularization, or alternatively called partial pooling \citep{gelman_bayesian_2013}. As opposed to fixed-effects estimation where a fixed-effects coefficient is determined exclusively with data from within a particular group, in a hierarchical model each of the group parameters are regularized towards a higher-level parameter estimated with the full data in proportion to the relative number of data points in a particular group.

The linear mixed effects models estimated by maximum likelihood that I use in the first section of this article also have have the regularization property. Bayesian estimation provides several theoretic advantages, such as correct inference in small samples and generalization to distributions other than the normal. However, for my purproses, the main benefit of using a Bayesian methodology is practical. I can fit a rich model with several hierarchies and many thousands of parameters, that simply can not be handled by maximum likelihood procedures.

The issue of how information asymmetries of quality affects market outcomes, first introduced by \citet{akerlof_market_1970} is one of the main topics in the modern industrial organization literature. Ch. 2 of \citet{tirole_theory_1988} and accompanying citation list provides a good overview of the theoretical foundations of this topic.

Early theoretical work of particular relevance to this paper includes \citet{chan_prices_1982}, whom model the situation where information on quality is costly rather than directly unavailable and where quality is endogenous to the seller--in other words the seller can choose the level of quality of its product. Under these assumptions, the authors predict several equilibrium--essentially markets for both high and low quality products depending on the extent to which the buyer is informed.

Reputation, or lack thereof, plays a particularly important role in this market. Most solar installers and panel manufacturers are relatively new firms, especially the increasingly dominant Chinese solar panel producers. \citet{shapiro_consumer_1982} explores the role of reputation, and finds that because reputation is effective only with a lag, the "steady-state" quality level chosen by a seller should be lower than in the scenario with perfect information.

An expanding empirical literatures exist on asymmetric information of quality, especially in the marketing, finance and accounting fields. In accounting, the issue of firm quality and voluntary disclosure in regulatory filings as a signal has received broad attention by empirical researchers. \citet{healy_information_2001} review the early literature. Empirical studies in finance have, for example, looked at issues of adverse-selection and quality in Initial Public Offerings \citep{michaely_pricing_1994}, small business lending \citep{petersen_benefits_1994}, and in a recent application for consumer credit markets \citep{dobbie_information_2013}.

The literature in the marketing field is also relevant to this paper, as it is particularly concerned with the effects of information asymmetry on purchases of consumer durables. The effects of signaling on quality, usually in the form of advertising, is particularly important in the field. \citet{kirmani_no_2000} provide an overview of this literature.

The use of leasing, discussed in this article, can be seen as a form of costly signaling about quality, however leasing plays more than just an informational role since it also transfers much of the risk of quality to the contractor. Traditionally, energy generation has been an activity undertaken by large, specialized firms with specialized knowledge and resources. The role of information asymmetry in investment and purchase decisions has likely been seen as a secondary issue, and to my knowledge, no literature exists on the role of such informational issues in the industry.

@@

For example \citet{dastrup_understanding_2012} argue that solar panels can not be considered a pure investment good, but are also bundled as a type of green conspicuous consumption, showing evidence for a ``solar price premium'' in homes with solar panels. \citet{bollinger_peer_2012} study the the role of peer effects in solar power adoption. They find evidence that the adoption of solar panels by homeowners in a certain zip-code will increase the probability that other households in that zip-code will install solar panels.

@@

The data used in this article is an intersection of two datasets from the California Solar Initiative (CSI). The California Solar Initiative is a state-wide program that gives incentives for installing grid-connected solar panels systems. The incentives are based on performance. For smaller systems, typical of most residential and small business installations, this incentive could be given in the form of an upfront payout based on the capacity and the expected performance of the system.

Larger systems were required to accept a performance based incentive based on actual production over 5 years (60 months). From the beginning of the program in 2007 this was defined as those over 100kW, but was lowered to 50kW from January 2008 and 30kW from January 2010. Solar panel installations of all sizes have the option of getting an incentive based on actual performance.

CSI provides data on all grid-connected solar panel systems installed in California since January 2007. In addition, CSI provides another data set of monthly production data from the solar panel systems that received production incentives. The data is openly available on the website of CSI. \footnote{\url{http://www.californiasolarstatistics.ca.gov/current_data_files/}}. A cleaned and merged data set that I use in the following analysis can be found on my website at \url{jmaurit.github.io#buy_or_lease}.

@@

I removed systems from the dataset that may have had reporting errors. for example I removed systems where production was reported to be higher than what would be theoretically possible from a solar power system with a given nameplate capacity. I also removed systems that reported 0 production in a period. This could also be an indication of quality if zero production indicates a malfunction in the system. However it is not possible to identify which zero observations reflect malfunctions versus reporting issues or other non-quality issues.

Table \ref{tbl:variables} gives an overview of the variables in the dataset that are used in the analysis. Notice that variables can vary by monthly observation or by solar power system. I will take account of this natural data hierarchy in my modeling. There are a total of 171,027 monthly observations used in the analysis. These observations come from 3,145 unique solar power systems. From these solar panel systems, panels from a total of 107 unique manufacturers are used.

@@

Production is measured in kilowatt hours (kWh). In the analysis, production data is first log transformed and then de-scaled, as shown in equation \ref{eqn:descaled}. For production data for each system, $s$, the log production data is demeaned and then divided by 2 times the standard deviation of the production data for that solar power system. Figure \ref{fig:production} gives a visualization of the transformed production data. The red line shows the average degradation over time of all the systems. The strong seasonality of production is also clearly visible.

Other continuous variables are transformed in a similar manner, with observation level variables de-scaled at the system level, and system-level variables de-scaled across systems. These transformations avoid confusion that may come when interpreting coefficients on variables with different units and scales. There are also technical reasons for the transformations relating to the MCMC routine. Convergence in the MCMC routine is aided when all variables are on the same scale. Setting appropriate weakly informative prior distributions on the parameters is also simplified when continuous variables are free from units.

@@

The cost per kilowatt (\$/kW) variable is the reported total cost of the solar panel system divided by the CSI capacity rating. For solar panel systems that are sold outright, the total cost is simply the transaction price of the entire system. For systems with third party owners, the total cost is an estimate reported by the system owner based on the sum of component costs, installation costs and a mark-up. I will discuss how this may effect the results.

@@

Finally, among the 3000 plus solar power systems, 497 had residential owners, 1759 had commercial owners, 777 had governmental owners and 112 had non-profit owners. A portion of the commercial owners operate as third-party-owners, with hosts in the other sectors. Alternatively, I could include host sector in my analysis: 1241 solar panel systems had a commercial host, 501 had a residential host, 1199 had a governmental host and 204 had a non-profit host. However, In a study of asymmetric information, it makes most sense to focus on the sector of the owner.

@@

\subsection{Testing for differences between module manufacturer}
Following the notation of \citet{bates_fitting_2015}, the conditional distribution of the response variables, $y$ in a linear mixed effects model can be written compactly as in equation \ref{equation:lme_simple}. Here $\mathbf{\beta}$ is a p-dimensional coefficient vector (or  ``fixed effects'') of the $n \times p$ matrix $\mathbf{X}$ of (p-1) explanatory variables plus intercept term. $\mathbf{Z}$ is an $n \times q$ model matrix of the variables whose groups are to be modeled directly with corresponding vector of coefficients, or ``random effects'' $\mathbf{B}$ that are fixed at values $\mathbf{b}$.\footnote{The use of ``random'' refers to the fact that these groups are assumed to be specific to the sample. Many applications of mixed effects model thus treat the varying group coefficients as group-level error-terms. Interpreting coefficients as group varying coefficients or as group error terms is mathematically equivalent.} Here $q$ is a dependent on the number of terms, $k$, that are allowed to vary by group and the number of groups, $l$ for each term: $q=\sum_i^k q_i = \sum_i^k l_i p_i$.  $\mathbf{W}$ is a diagonal matrix of known prior weights. $B$ is distributed as multinomial normal with zero mean and where $\Sigma$ is variance-covariance matrix.

@@

To test whether I can detect quality differences between module manufacturers, I need to first estimate a restricted comparison model. I write the restricted comparison model explicitly in equation \ref{eqn:observation_level_rest}.

In this model, the transformed production variable, $prod\_scaled_{i}$ for observation $i$ is distributed normally with the mean modeled as a linear function of an intercept term $a_s$, a slope term, $b_s$ on the transformed months of operation variable $months\_operation\_scaled$, and a set of dummy variables representing the month of year, $\mathbf{month}$. Notice that the intercept and slope are indexed by $s$, indicating that they are allowed to vary by the individual system. Thus in this model formulation I take into account the groupings by system, explicitly modeling varying relative initial production values (intercepts) and degradation over time (slope). Moving up a level, the estimated $a$ and $b$ parameters are in turn modeled as multivariate normal.

\begin{equation}
\begin{aligned}
prod_{i} &\sim N(\mathbf{month} + a_s + b_s months\_operation\_scaled_{i}, \sigma^2)\\
\begin{pmatrix}
  a\\
  b
\end{pmatrix}
&\sim N
\begin{pmatrix}
  \mu_a\\
  \mu_b
\end{pmatrix},
\begin{pmatrix}
  \sigma_a^2 & \rho \sigma_a \sigma_b \\
  \rho \sigma_a \sigma_b & \sigma_b^2
\end{pmatrix}\label{eqn:observation_level_rest}
\end{aligned}
\end{equation}

The inclusion of the matrix of month dummies, $\mathbf{\mu^{month}}$, controls for seasonal variation across all systems. This is a simplified way to model seasonality, but because the data is itself at a monthly frequency, and a more direct modeling of seasonality is not of direct importance, this should suffice. As long as un-modeled variation in seasonality is not correlated with the long-run slope of production, the point estimates for the slope should be unbiased.

>>>>

%All floats at end.
% \usepackage[nomarkers]{endfloat}

%keywords
\providecommand{\keywords}[1]
{
  \small
  \textbf{\textit{Keywords---}} #1
}

\title{Are Solar Panels Commodities? A Bayesian Hierarchical Approach to Detecting Quality Differences and Asymmetric Information.}
\author{Johannes Mauritzen\thanks{BI Norwegian Business School, johannes.mauritzen@bi.no, \url{http://jmaurit.github.io}}}

@@

\begin{abstract}
Solar panels should not be considered commodities. Considerable quality differences, as measured directly by degradation of production over time, are found between manufacturers. I test two implications from the theory of asymmetric information of quality and find: 1.) Solar power systems with high-information third-party owners display higher quality than host-owned systems. 2.) Furthermore, with a 85\% probability, the price of solar panels that are owned by high-information owners are more highly correlated to quality. Methodologically, the article demonstrates a novel application of Bayesian hierarchical regression models that are increasingly popular in operations research and the decision sciences.
\end{abstract}

%TC:ignore
\keywords{Solar power, commodities, asymmetric information, quality, Bayesian hierarchical model}

@@

More formally, a commodity is generally defined by a certain degree of fungibility. That is, the good from a certain producer will be largely interchangeable with the good of another producer. Already in 1873 the German economist A.E.F. Schäffle distinguished between a popular understanding of a commodity as a material input in manufacturing, to the scientific understanding as "exchangeable material goods" \citep{menger_principles_2007}. Despite the simplicity of this definition, \citet{gordon_what_1999} show the difficulty in practice of determining whether a product is in fact a commodity. The root problem is that a good can be differentiated in a host of ways, some of which are difficult to observe at the time of transaction.

Determining whether a product is a commodity is of more than just theoretical importance. Historically, the commodification of goods was a necessary condition for the establishment of sophisticated financial markets for those goods. A well-documented example: The invention of grain elevators for mixing and standardising grain was a necessary precursor to the establishment of a futures markets with receipts of delivery traded on the Chicago Board of Trade \citep{cronon_natures_1992}. The abstraction between producer and end purchaser of goods was necessary for the functioning of these markets. A trader could fulfil a promise to deliver grain of a certain grade by simply buying it on the market or with cash settlement, rather than having produced it oneself.

@@

From the perspective of a purchasing manager responsible for procuring solar panels, whether panels can be considered a commodity is of great importance. If panels are known to be commodities with standardised quality and similar pricing, then the decision for purchasing manager is substantially simplified. They need only to decide on the observable form factor, for example dimension and capacity. In addition, purchasing managers responsible for large projects with long lead times could make use of forward markets to hedge price movements. On the other hand, if solar panels are known to vary significantly by quality, then the decision becomes substantially more complex and costly. Purchasing managers would need to weigh the price of panels against expected quality. They may also need to make use of specialised engineering firms that test and certify panel quality. Since the purchasing decision is likely to be linked to a specific manufacturer, the purchasing manager is subject to risks such as bankruptcy or other supply disruption associated with that firm.

Furthermore, if significant quality differences between manufacturers exists, then the characteristics of solar panel investments suggest the possibility of asymmetric information of quality in the market. This is important in practice, since the presence of information asymmetry in a market tends to lead to the persistence of low quality suppliers.

@@

The market for rooftop solar panels can be expected to be particularly vulnerable to issues of asymmetric information on quality. Solar panels can be characterised as an ``experience'' good, where an investor/consumer needs to learn about the quality through use \citep{caulkins_interaction_2017}. In particular, poor quality panels will tend to show a higher degradation of output over time than high quality panels. Even then, solar panel owners may find it difficult to measure the degradation as it can happen gradually, over many years.

@@

From this informal model of information asymmetry in the market for solar panels, a testable implication arises. The quality of panels, as measured by degradation of output over time, would be predicted to be higher in the systems owned by the high-information owners (third-party-owner) who can discern between low and high quality solar panels. Conversely, the basic theory of asymmetric information suggests that lower quality panels will tend to push out higher quality panels in the presence of low-information buyers who cannot discern quality, and therefor make purchasing decision solely on price.

A related prediction from the theory of asymmetric information of quality is that the cost of solar panel systems should have a higher degree of correlation with quality when the owner is a high-information type. Because a high-information owner can, by definition, differentiate between high- and low-quality panels.

@@

In summary, I have three nested research hypothesis that I wish to test empirically.

@@

The data has a natural hierarchy of between 36 and 60 monthly observations within the 3000-plus solar panel systems, which in turn can be grouped according to relevant characteristics such as whether they are host-owned or third-party owned. Because these groupings display considerable heterogeneity in sample size, mean values and variance, it is natural to model the relevant structure of the data directly. For relatively parsimonious models with one or two hierarchies and few covariates, I can use standard linear mixed effects models (LMEM) estimated by maximum likelihood. However, for richer models with all relevant hierarchies, maximum likelihood becomes impractical.

%Berger - statistical decision theory.

As a solution, I use a Bayesian hierarchical\footnote{Sometimes also called multilevel modell} model estimated using Markov Chain Monte Carlo (MCMC) simulation techniques. Bayesian hierarchical models have long been one of the primary tools in statistical decision theory \citep{berger_statistical_1985} and this form of modelling is increasingly common in operations research and management science. One of the main advantages is superior out-of-sample predictive properties with data with distinct groupings. Recent advances in computation have also allowed for the construction and simulation of increasingly complex models. In particular, I use the Stan probabilistic programming language \citep{stan_development_team_stan_2014} that makes use of Hamiltonian Markov Chain Monte Carlo (MCMC) \citep{mackay_information_2003} and a No-U-Turn sampler \citep{homan_no-u-turn_2014}. Unlike earlier MCMC simulation routines, notably Gibbs sampler, Hamiltonian MCMC is able to reach convergence even with models, like the one I present in this article, with multiple hierarchies. Importantly, with the Hamiltonian MCMC routine, it is not necessary to use conjugate distributions, opening up to a wider variety of choice of prior distributions \citep{kruschke_doing_2014}.

In part due to increasing computational tractability, Bayesian hierarchical models have recently become a common and useful tool in the operations research field. A common application is to incorporate expert opinion into quantitative decision models \citep{rufo_merging_2010, szwed_bayesian_2006, utkin_method_2006}. In this application, the Bayesian hierarchical model is flexible enough to aggregate the information of the expert opinions while also being able to explicitly handle and propagate the uncertainty in these opinions. Hierarchical models have also been used to identify default risk among lenders and improve credit scoring models \citep{liu_identifying_2015, bhattacharya_bayesian_2019}. In this context, the hierarchical Bayesian models are found to provide superior out-of-sample prediction for the censored sample of the data. Other operations research related applications include a fund manager's portfolio selection problem \citep{soyer_bayesian_2006, bodnar_bayesian_2017} and conjoint analysis in operations management \citep{karniouchina_issues_2009, gensler_willingness--pay_2012}. A commonality among all these applications is the need to aggregate information from heterogenous groups without over-fitting the data with many fixed effects.

Despite the usefulness of hierarchical Bayesian models, examples of hierarchical models in the economics and finance literature are sparse. \citet{dehejia_was_2003} uses a Bayesian hierarchical model to evaluate the effectiveness at multiple programs at different sites. By incorporating ``predictive uncertainty'' by way of a hierarchical model, the impact of the sites, which otherwise is estimated to be significant with a fixed effects model, disappears. \citet{meager_understanding_2018} uses a hierarchical model to aggregate studies of micro-credit expansion in developing countries in order to estimate an overall treatment effect with ``external validity,'' that is the degree to which an estimated treatment effect generalizes to other populations. \citet{jones_mutual_2005} uses a hierarchical model to study returns of mutual funds, arguing that estimates of long-run returns of any single fund should be informed, by way of a higher-level distribution, of the returns of the population of other mutual funds. In a study with parallels to my own, \citet{korteweg_skill_2017} uses a Bayesian hierarchical model to study persistence of returns in the private equity sector both between and within firms, where persistence is measured by excess variation between firms as captured by firm-level parameters (or random effects) that are drawn from a higher-level distribution. If returns are thought of as the converse of production degradation, then the existence of persistence of returns can be thought of as the converse of quality differences.

@@

The property of hierarchical models that allows for improved predictive performance with the presence of groupings in the data is regularization, or alternatively called partial pooling \citep{gelman_bayesian_2013}. As opposed to fixed effects estimation where a fixed effects coefficient is determined exclusively with data from within a particular group, in a hierarchical model each of the group parameters are regularized towards a higher-level parameter estimated with the full data in proportion to the relative number of data points in a particular group.

The linear mixed effects models estimated by maximum likelihood that I use in the first section of this article also have the regularization property. Bayesian estimation provides several theoretic advantages, such as correct inference in small samples and generalization to distributions other than the normal. However, for my purposes, the main benefit of using a Bayesian methodology is practical. I can fit a rich model with several hierarchies and many thousands of parameters, that simply cannot be handled by maximum likelihood procedures.

The issue of how information asymmetries of quality affects market outcomes was first introduced by \citet{akerlof_market_1970}. Ch. 2 of \citet{tirole_theory_1988} and accompanying citation list provides a good overview of the theoretical foundations of this topic.

Early theoretical work of particular relevance to this paper includes \citet{chan_prices_1982}, whom model the situation where information on quality is costly rather than directly unavailable and where quality is endogenous to the seller--in other words the seller can choose the level of quality of its product. Under these assumptions, the authors predict several equilibrium--essentially markets for both high- and low-quality products depending on the extent to which the buyer is informed.

Reputation, or lack thereof, plays a particularly important role in this market. Most solar installers and panel manufacturers are relatively new firms, especially the increasingly dominant Chinese solar panel producers. \citet{shapiro_consumer_1982} explores the role of reputation and finds that because reputation is effective only with a lag, the "steady-state" quality level chosen by a seller should be lower than in the scenario with perfect information.

An expanding empirical literature exists on asymmetric information of quality, especially in the marketing, finance and accounting fields. In accounting, the issue of firm quality and voluntary disclosure in regulatory filings as a signal has received broad attention by empirical researchers. \citet{healy_information_2001} review the early literature. Empirical studies in finance have, for example, looked at issues of adverse-selection and quality in Initial Public Offerings \citep{michaely_pricing_1994}, small business lending \citep{petersen_benefits_1994}, and in a recent application for consumer credit markets \citep{dobbie_information_2013}.

The literature in the marketing field is also relevant to this paper, as it is particularly concerned with the effects of information asymmetry on purchases of consumer durables. The effects of signalling on quality, usually in the form of advertising, is particularly important in the field. \citet{kirmani_no_2000} provide an overview of this literature.

The use of leasing, discussed in this article, can be seen as a form of costly signalling about quality. However leasing plays more than just an informational role since it also transfers much of the risk of quality to the contractor. Traditionally, energy generation has been an activity undertaken by large, specialized firms with specialized knowledge and resources. The role of information asymmetry in investment and purchase decisions has likely been seen as a secondary issue, and to my knowledge, no literature exists on the role of such informational issues in the industry.

@@

For example \citet{dastrup_understanding_2012} argue that solar panels cannot be considered a pure investment good, but are also bundled as a type of green conspicuous consumption, showing evidence for a ``solar price premium'' in homes with solar panels. \citet{bollinger_peer_2012} study the the role of peer effects in solar power adoption. They find evidence that the adoption of solar panels by homeowners in a certain zip-code will increase the probability that other households in that zip-code will install solar panels. A focus in the operations research field has been on designing systems to manage and aggregate such distributed energy resources on behalf of un-sophisticated owners \citep{velik_energy_2016, le_cadre_gametheoretic_2019}.

@@

The data used in this article is an intersection of two data-sets from the California Solar Initiative (CSI). The California Solar Initiative is a state-wide program that gives incentives for installing grid-connected solar panel systems. The incentives are based on performance. For smaller systems, typical of most residential and small business installations, this incentive could be given in the form of an upfront pay-out based on the capacity and the expected performance of the system.

Larger systems were required to accept a performance-based incentive based on actual production over 5 years (60 months). From the beginning of the program in 2007 this was defined as those over 100 kW, but was lowered to 50 kW from January 2008 and 30 kW from January 2010. Solar panel installations of all sizes have the option of getting an incentive based on actual performance.

CSI provides data on all grid-connected solar panel systems installed in California since January 2007. In addition, CSI provides another data set of monthly production data from the solar panel systems that received production incentives. The data is openly available on the website of CSI. \footnote{\url{http://www.californiasolarstatistics.ca.gov/current_data_files/}}. %A cleaned and merged data set that I use in the following analysis can be found on my website at \url{jmaurit.github.io#buy_or_lease}.

@@

I removed systems from the data that may have had reporting errors. For example, I removed systems where production was reported to be higher than what would be theoretically possible from a solar power system with a given nameplate capacity. I also removed systems that reported 0 production in a period. This could also be an indication of quality if zero production indicates a malfunction in the system. However, it is not possible to identify which zero observations reflect malfunctions versus reporting issues or other non-quality issues.

Table \ref{tbl:variables} gives an overview of the variables in the data that are used in the analysis. Notice that variables can vary by monthly observation or by solar power system. I will take account of this natural data hierarchy in my modelling. A total of 171,027 monthly observations are used in the analysis. These observations come from 3,145 unique solar power systems. From these solar panel systems, panels from a total of 107 unique manufacturers are used.

@@

Production is measured in kilowatt hours (kWh). In the analysis, production data is de-scaled, as shown in equation \ref{eqn:descaled}.  For production data for each system, $s$, the production data observations for each month, $i$, is demeaned and then divided by the standard deviation of the production data for that solar power system. Figure \ref{fig:production} gives a visualization of the transformed production data. The red line shows the average degradation over time of all the systems. The strong seasonality of production is also clearly visible.

Other continuous variables are transformed in a similar manner, with observation-level variables de-scaled at the system level, and system-level variables de-scaled across systems. These transformations avoid confusion that may come when interpreting coefficients on variables with different units and scales. There are also technical reasons for the transformations relating to the MCMC routine. Convergence in the MCMC routine is aided when all variables are on the same scale. Setting appropriate weakly informative prior distributions on the parameters is also simplified when continuous variables are free from units.

@@

The cost per kilowatt (\$/kW) variable is the reported total cost of the solar panel system divided by the CSI capacity rating. For solar panel systems that are sold outright, the total cost is simply the transaction price of the entire system. For systems with third party owners, the total cost is an estimate reported by the system owner based on the sum of component costs, installation costs and a mark-up. I will discuss how this may affect the results.

@@

Finally, among the 3145 plus solar power systems, 497 had residential owners, 1759 had commercial owners, 777 had governmental owners and 112 had non-profit owners. A portion of the commercial owners operate as third-party-owners, with hosts in the other sectors. Alternatively, I could include host sector in my analysis: 1241 solar panel systems had a commercial host, 501 had a residential host, 1199 had a governmental host and 204 had a non-profit host. However, in a study of asymmetric information, it makes most sense to focus on the sector of the owner.

@@

\subsection{Testing for differences between module manufacturer}
Following the notation of \citet{bates_fitting_2015}, the conditional distribution of the response variables, $y$ in a linear mixed effects model can be written compactly as in equation \ref{equation:lme_simple}. Here $\mathbf{\beta}$ is a p-dimensional coefficient vector (or  ``fixed effects'') of the $n \times p$ matrix $\mathbf{X}$ of (p-1) explanatory variables plus intercept term. $\mathbf{Z}$ is an $n \times q$ model matrix of the variables whose groups are to be modelled directly with corresponding vector of coefficients, or ``random effects'' $\mathbf{B}$ that are fixed at values $\mathbf{b}$.\footnote{The use of ``random'' refers to the fact that these groups are assumed to be specific to the sample. Many applications of mixed effects model thus treat the varying group coefficients as group-level error-terms. Interpreting coefficients as group varying coefficients or as group error terms is mathematically equivalent.} Here $q$ is dependent on the number of terms, $k$, that are allowed to vary by group and the number of groups, $l$, for each term: $q=\sum_i^k q_i = \sum_i^k l_i p_i$.  $\mathbf{W}$ is a diagonal matrix of known prior weights. $B$ is distributed as multinomial normal with zero mean and where $\Sigma$ is variance-covariance matrix.

@@

To test whether I can detect quality differences between module manufacturers, I need to first estimate a restricted comparison model. I write the restricted comparison model explicitly in equation \ref{eqn:observation_level_rest}. Symbols are defined in table \ref{tbl:definitions3p1}.

In this model, the transformed production variable, $prod\_scaled_{i}$ for observation $i$ is distributed normally with the mean modelled as a linear function of an intercept term $a_s$, a slope term, $b_s$ on the transformed months of operation variable $months\_operation\_scaled$, and a set of dummy variables representing the month of year, $\mathbf{month}$. Notice that the intercept and slope are indexed by $s$, indicating that they are allowed to vary by system. Thus, in this model formulation, I take into account the groupings by system, explicitly modelling varying relative initial production values (intercepts) and degradation over time (slope). Moving up a level, the estimated $a$ and $b$ parameters are in turn modelled as multivariate normal distributions.

\begin{table}
  \begin{tabular}{rl}
  \toprule
    Symbol &  Definition \\
    \midrule
    $prod_i$ & Production from a given system in a given month (observation i), descaled\\
    $\mathbf{month}$ & Vector of month dummy variables\\
    $months\_operation_i$ & Number of months of operation of a system at observation i, descaled \\
    $\mathbf{a_s}$& Intercept parameter for a system, s \\
    $\mathbf{b_s}$ & Slope parameter for a system, s \\
    $\sigma^2$ & Variance of the production data \\
    $\mu^a$ & Mean of the system intercept terms, $a_s$ \\
    $\mu^b$ & Mean of the system slope terms, $b_s$ \\
    $\sigma^{2,a}$ & Variance of the system intercept terms, $a_s$ \\
    $\sigma^{2,b}$ & Variance of the system slope terms, $b_s$ \\
    $\rho$ & Correlation coefficients between intercept and slope terms \\

  \bottomrule
  \end{tabular}
  \caption{Definitions from the restricted model presented in equation \ref{eqn:observation_level_rest}. \label{tbl:definitions3p1}}
\end{table}
